Synaptic connectome of the ctenophore apical organ

### 2025-02-17 manuscript/Manuscript.qmd
Subtitle

---
title: "Synaptic connectome of the ctenophore apical organ"
subtitle: |
  \raggedright  Kei Jokura^1,2,4,5\*^, Sanja Jasek^1,3,4^,  Lara Kewalow^3^, Pawel Burkhardt^6^, Gáspár Jékely^1,3,4,\*^  \newline<br>^1^Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom \newline<br>^2^Exploratory Research Center on Life and Living Systems (ExCELLS), National Institutes of Natural Sciences, Okazaki, Japan\newline<br>^3^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^4^BioSciences, University of Exeter, Stocker Road, Exeter EX4 4QD, Exeter, United Kingdom\newline<br> ^5^National Institute for Basic Biology (NIBB), National Institutes of Natural Sciences, Okazaki, Japan\newline<br>^6^Michael Sars Centre, University of Bergen, Norway \newline<br> ^\*^Correspondence:  jokura@nibb.ac.jp, gaspar.jekely@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html:
    embed-resources: true 
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

>>>>

---
title: "Synaptic connectome of the ctenophore apical organ"

subtitle: |
  **Kei Jokura**$^{1,2,3,*}$, **Sanja Jasek**$^{1,4}$, **Lara Kewalow**$^{4}$, **Pawel Burkhardt**$^{5}$, **Gáspár Jékely**$^{1,4,*}$  
  <br><br>  
  $^{1}$ Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom  
  <br>  
  $^{2}$ Exploratory Research Center on Life and Living Systems (ExCELLS), Okazaki, 444-8787, Japan  
  <br>  
  $^{3}$ National Institute for Basic Biology (NIBB), Okazaki, 444-8585, Japan  
  <br>  
  $^{4}$ Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany  
  <br>  
  $^{5}$ Michael Sars Centre, University of Bergen, Norway  
  <br><br>  
  **$^{*}$ Correspondence:**  
  [jokura@nibb.ac.jp](mailto:jokura@nibb.ac.jp),  
  [gaspar.jekely@cos.uni-heidelberg.de](mailto:gaspar.jekely@cos.uni-heidelberg.de)

mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html:
    embed-resources: true 
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---
